Data Specialization for a Staged Lambda Calculus

### 2015-02-09 paper/figures/splitting-overview.tex
implemented some kayvon comments

\hspace{2em} Evaluation Rule: $\sepredtwo {\pipeM c l r} {\mval i {[b/l]r}}$, where $b$ (also the {\em boundary value}) is generated by $\reduce c (i,b)$

>>>>

\hspace{2em} Evaluation Rule: $\sepredtwo {\pipeM c l r} {\mval i {[b/l]r}}$, where $b$ (also called the {\em boundary value}) is generated by $\reduce c (i,b)$
